\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2020-01-09 gwnnDraft02.tex
Added in body text dealing with referee

The exotic sectors have essentially massless degrees of freedom pre-phase transition and pions with negligible masses post-phase transition. Other composite particles, such as baryons, do gain a mass of the order of $\Lambda_{ex}$; this is, however, still much smaller than the order of $\rho_R$ leading to small $\alpha_{\infty}$ according to Eq.~(\ref{eqn:critPTstrength}).\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors, their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.} Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales. They do, however, feature glueballs that obtain a mass of the order of the SFOPT and, just as in the case for exotic sectors above, feature small $\alpha_{\infty}$. Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime. 
%Explicitly, all exotic sectors (and heavy standard sectors) have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). 
Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$. In this case, the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.

>>>>

The exotic sectors have essentially massless degrees of freedom pre-phase transition and pions with negligible masses post-phase transition. Other composite particles, such as baryons, do gain a mass of the order of $\Lambda_{ex}$; this is, however, still much smaller than the order of $\rho_R$ leading to small $\alpha_{\infty}$ according to Eq.~(\ref{eqn:critPTstrength}).\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors, their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.} Heavy standard sectors that undergo SFOPT for QCD feature no baryons due to all quarks being above their respective QCD scales. They do, however, feature glueballs that obtain a mass of the order of the SFOPT and, just as in the case for exotic sectors above, feature small $\alpha_{\infty}$. Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime. 
%Explicitly, all exotic sectors (and heavy standard sectors) have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). 
Each component of the spectral energy density in Eq.~(\ref{eqn:SpectralEng}) is proportional to a power of their respective efficiency factors $\kappa$. The relative strength of the efficiency factors is dependent on the ratio $\frac{\alpha_{\infty}}{\alpha}$ --- since $\alpha_{\infty}$ is small, this would typically lead to the a scenario where the efficiency factors for the sound wave and MHD contributions are small and the GWs produced are dominantly from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$: this is what we assume for the remainder of this section. It should be noted, however, that $\alpha$ can be small \cite{Bai:2018dxf,Helmboldt:2019pan}; this leads to the non-bubble collision contributions being important and changes the GW profile. This case and the gravitational waves it produces are examined in the appendix.
